
# Matrices, Arrays, Data frames

## Lecture slides

```{r, comment=NA, message=FALSE, echo=FALSE}
knitr::include_url("https://hellor.netlify.app/slides/l22021.html#1")

#<iframe seamless width="500%" height="500%" frameborde="0" #src="https://hellor.netlify.app/2021/week1/l12021.html#1"></iframe>

```


## Matrices

Use the code below to create the vector `uniform.values`.

```{r}
set.seed(21)
uniform.values <- runif(50)
uniform.values
```
 
1. Arrange data in `uniform.values` according to the following formats:

  (a) single row matrix.
    
  (b) single column matrix
    
  (c) matrix $5 \times 10$ 
    
  (d) matrix $10 \times 5$ 
  
2. Write the code to output the following matrix.

```{r, comment=NA, echo=FALSE}
rnames <- c("a", "b")
cnames <- rep(NA, 25)
a <- matrix(uniform.values, byrow=TRUE, nrow=2, dimnames = list(rnames))
a
```

3. Matrix visualization: The matrix `m` contains 70 randomly generated values from the $Unif(0, 1)$ distribution. The R function `image` is used to visualize the matrix.  

```{r, comment=NA}
set.seed(1)
values <- runif(70)
m <- matrix(values, 10, 7)
m
image(m, useRaster=TRUE, axes=FALSE)
```

a) Record the values in the matrix (m) as follows: matrix value = 0 if value lessthan 0.5 and 1 otherwise. Write an R code to visualize the new matrix.

```{r, comment=NA, echo=FALSE, eval=FALSE}
m[m < 0.5] <- 0
m[m >=0.5] <- 1
image(m, useRaster=TRUE, axes=FALSE)

```

b) Consider the matrix `ymat` given below. Convert all even index position values to 0 and odd position values to 1. 

```{r, echo=FALSE}
ymat <- matrix(1:100, ncol=10, nrow = 10) *10
```

```{r, echo=FALSE, comment=NA}
ymat
```

 

Help:

```{r, comment=NA}
5 %% 2
6 %% 2
```

Visualize the matrix using the `image` function. Your output should look like this:

```{r, echo=FALSE}
ymat <- ymat/10
ymat <- ymat %% 2
image(ymat, useRaster=TRUE, axes=FALSE)
```

## Array

Write R codes to create the following arrays.

(a)

```{r, comment=NA, message=FALSE, echo=FALSE}
# Create two vectors of different lengths.
vector1 <- c(1, 2, 3)
vector2 <- c(10,11,12,13,14,15)
column.names <- c("COL1","COL2","COL3")
row.names <- c("ROW1","ROW2","ROW3")
matrix.names <- c("Matrix1","Matrix2")

# Take these vectors as input to the array.
result <- array(c(vector1,vector2),dim = c(3,3,2),dimnames = list(row.names,column.names,
   matrix.names))
result
```

(b)

```{r, comment=NA, message=FALSE, echo=FALSE}
array(2:13, dim = c(2, 3, 2))
```


## Dataframe

1. Store the following values into a data frame.





