# Data Visualization with R: qplot

## Lecture Slides


```{r, comment=NA, message=FALSE, echo=FALSE}
knitr::include_url("https://hellor.netlify.app/slides/l42021.html#1")

#<iframe seamless width="500%" height="500%" frameborde="0" #src="https://hellor.netlify.app/2021/week1/l12021.html#1"></iframe>

```

## Visualizing the `diamonds` dataset using R


This question is based on diamonds dataset in `ggplot2` package. Load the `ggplot2` package and the `diamonds` dataset using the following command.

```{r, comment=NA, echo=TRUE, message=FALSE, warning=FALSE}
library(ggplot2)
data("diamonds")
```


To find out what information there is about the dataset, you can run the command:

```{r, comment=NA, echo=TRUE, eval=FALSE}
help(diamonds)
```


There are over 50000 observations and 10 variables in the diamond dataset. Write down the R codes to reproduce the following graphic outputs.

a. 

```{r, comment=NA, message=FALSE, echo=FALSE}
library(ggplot2)
data(diamonds)
qplot(color, data = diamonds, geom = "bar", fill = color, alpha = 0.5) 
```

Help: use `fill` option to assign colours and `alpha` option to add transparency to the bars.

b. 

```{r, comment=NA, message=FALSE, echo=FALSE}
qplot( data = diamonds, carat, price, geom = c("point", "smooth"))
```

Help: use geoms, `point` and `smooth`.

c. 

```{r, comment=NA, echo=FALSE}
qplot(data = diamonds, x = price, color = color, geom = 'boxplot' )

```

d. 


```{r, comment=NA, echo=FALSE}
qplot(data = diamonds, y = price, color = color, geom = 'boxplot' )

```

e. 


```{r, comment=NA, echo=FALSE}
qplot(data = diamonds, y = price, fill = color, geom = 'boxplot' )

```

f. 

```{r, comment=NA, message=FALSE, echo=FALSE}
qplot( data = diamonds, carat, price, colour=color, geom = "point")
```

g. 

```{r, comment=NA, message=FALSE, echo=FALSE}
qplot( data = diamonds, carat, price, colour=color, geom = c("point", "smooth"))
```


\newpage


## Answers 
    
**Section 4.3**

a. 

```{r, comment=NA, message=FALSE, eval=FALSE}
library(ggplot2)
data(diamonds)
qplot(color, data = diamonds, geom = "bar", fill = color, alpha = 0.5) 
```



b. 

```{r, comment=NA, message=FALSE, eval=FALSE}
qplot( data = diamonds, carat, price, geom = c("point", "smooth"))
```



c. 

```{r, comment=NA, eval=FALSE}
qplot(data = diamonds, x = price, color = color, geom = 'boxplot' )

```

d. 


```{r, comment=NA, eval=FALSE}
qplot(data = diamonds, y = price, color = color, geom = 'boxplot' )

```

e. 


```{r, comment=NA, eval=FALSE}
qplot(data = diamonds, y = price, fill = color, geom = 'boxplot' )

```

f. 

```{r, comment=NA, message=FALSE, eval=FALSE}
qplot( data = diamonds, carat, price, colour=color, geom = "point")
```

g. 

```{r, comment=NA, message=FALSE, eval=FALSE}
qplot( data = diamonds, carat, price, colour=color, geom = c("point", "smooth"))
```


    
    



